Equalizer\\Programming and User Guide

### 2009-08-08 Developer/ProgrammingGuide/paper.tex
Final version of 0.9 Programming and User Guide
[ ] Will break Win32 build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.6 RC1 for Equalizer 0.9\\[\medskipamount]
%  \today
}

@@

OpenGL is a registered Trademark, OpenGL Multipipe is a Trademark of
Silicon Graphics, Inc. Linux is a registered Trademark of Linus
Torvalds.  Mac OS is a Trademark of Apple Inc. CAVELib is a registered
Trademark of the University of Illinois. The CAVE is a registered
Trademark of the Board of Trustees of the University of Illinois at
Chicago. Qt is a registered Trademark of Trolltech. TripleHead2Go is a
Trademark of Matrox Graphics. PowerWall is a Trademark of Mechdyne
Corporation. All other trademarks and copyrights herein are the property
of their respective owners.

@@

If you have comments about the content, accuracy or comprehensibility of
this programming guide, please contact
\htmladdnormallink{eile@eyescale.ch}
{mailto:eile@eyescale.ch?subject=Equalizer\%20Programming\%20Guide}.

@@

The images on the front page show the following applications build using
Equalizer: RTT DeltaGen\footnote{Image copyright Realtime Technology AG,
  2008} [top left], a flow visualization application for climate
research\footnote{Image courtesy of Computer Graphics and Multimedia
  Systems, University of Siegen}, the \textsf{eVolve} volume
renderer\footnote{Data set courtesy of General Electric, USA} [bottom
left] the \textsf{eqPly} polygonal renderer in a three-sided CAVE
[bottom center], and a six-node sort-last database decomposition with
parallel direct-send recomposition\footnote{Data set courtesy of
  Stanford University Computer Graphics Laboratory} [bottom right].

The images on the back page show the following scalable rendering modes:
2D (sort-first, SFR), DB (sort-last), stereo, pixel and DPlex
(time-multiplex, AFR).

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
\listoffigures \vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6 RC1 & Jul 31, 2009 & Release Candidate 1 for Equalizer 0.9\\
    \hline
  \end{tabularx}}
\clearpage

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.6 for Equalizer 0.9\\[\medskipamount]
%  \today
}

@@

OpenGL is a registered Trademark, OpenGL Multipipe is a Trademark of
Silicon Graphics, Inc. Linux is a registered Trademark of Linus
Torvalds.  Mac OS is a Trademark of Apple Inc. CAVELib is a registered
Trademark of the University of Illinois. The CAVE is a registered
Trademark of the Board of Trustees of the University of Illinois at
Chicago. Qt is a registered Trademark of Trolltech. TripleHead2Go is a
Trademark of Matrox Graphics. PowerWall is a Trademark of Mechdyne
Corporation. CUDA is a Trademark of NVIDIA Corporation. All other
trademarks and copyrights herein are the property of their respective
owners.

@@

If you have comments about the content, accuracy or comprehensibility of
this Programming and User Guide, please contact
\htmladdnormallink{eile@eyescale.ch}
{mailto:eile@eyescale.ch?subject=Equalizer\%20Programming\%20Guide}.

@@

The images on the front page show the following applications build using
Equalizer: 
RTT DeltaGen\footnote{Image copyright Realtime Technology AG, 2008} [top
right], 
\textsf{eqRaster}, a scalable terrain visualization\footnote{Image
  courtesy of Visualization and Multimedia Lab, University of Zurich}
[middle center],
a flow visualization application for climate research\footnote{Image
  courtesy of Computer Graphics and Multimedia Systems, University of
  Siegen} [middle right],
the \textsf{eqPly} polygonal renderer in a three-sided CAVE [bottom
left],
the \textsf{eVolve} volume renderer\footnote{Data set courtesy of
  General Electric, USA} [bottom center],
and the \textsf{eqNBody} gravitational n-body simulation, based on the
N-Body CUDA example [bottom right].

The images on the back page show the following scalable rendering modes:
Combined 2D/DB [top left], DPlex [middle left], Pixel [middle center],
2D [bottom left], DB [bottom center] and stereo [bottom right].

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
\listoffigures \vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    \hline
  \end{tabularx}}
\clearpage
